Minimizing post-shock forecasting error through aggregation of outside information

### 2021-01-27 Revision/manuscript.tex
revised manuscript and list with changes in red
made what I am hoping is the last or second to last round of edits. Please look over carefully.

In our methodological framework, the researcher creates a synthetic panel of time series which have undergone similar structural shocks in the past. Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}. As in SCM, care is needed when forming the donor pool of time series. However, there are key differences between our framework and SCM. We assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock. Moreover, the shocks from candidate time series in the donor pool, together with the shock in the time series of interest, are assumed to be  from a common family of distributions with existing second moments.

We then estimate the shock effects that are present in the time series forming the donor pool for which post-shock responses are observed. These estimated shock effects are then aggregated and this aggregated estimator is taken to be the estimator for the shock effect in the time series of interest. Finally, this aggreagted estimator is then added to a forecast for the yet to be realized post-shock response of the time series of interest. Our adjustment is similar to various adjustment methodologies suggested by \cite{clements1996intercept} that use the residual at end of observed time horizon for $h$-ahead forecasts. However, the approach of \cite{clements1996intercept} is not robust to unprecedented and unobserved shock since the shock signal is not embedded in the data. Under a similar setting that studies equilibrium shifts, \cite{castle2015robust} propose robust general approaches for forecasting in vector equilibrium-correction models. However, their forecasting methodology requires conditioning on the past data that contain shock signals. This approach is therefore not applicable in the post-shock setting.

The shock effects in our post-shock forecasting framework are similar to ``expectation shocks,'' studied in \cite{clements2019measuring}. \cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach, as in \cite{croushore2006data}. In our context, the yet to be observed shock effect of interest arises as a random effect whose assumed generative distribution can only be partially estimated. This partial estimation only uses shock effect estimates from the time series forming the donor pool.

In this article, we will assume a simple autoregressive data generating process  with a general random-effect structure. These specifications are similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical}. In our model, the donor pool can consist of dependent time series, but the time series forming the donor pool are required to be independent from the time series of interest. However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method. We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. Our autoregressive model will consider present day covariates to better motivate similarity weighting. The considered adjustment strategies all target the mean of the shock effect distribution. Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop. We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.  We demonstrate the utility of our methodology with two real data analyses. The first of these focuses on forecasting the stock price of Conoco Phillips after March 9th, 2020, in the midst of the COVID-19 pandemic and an oil supply war. The second of these focuses on forecasting the stock price of Apple Inc. after the company releases their latest installment of the MacBook on November 10th, 2020. We will show that our proposed adjustment estimators yield much better results than no adjustment in these settings. The example of Conoco Phillips provides an empirical application of our methods in unprecedented shocks whereas the Apple example provides a case for post-shock prediction where the shock has precedent. We now motivate our framework for post-shock prediction.

@@

Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation procedure for evaluation of these conditions, discussed in Section \ref{conditions} and \ref{varbootstrap} respectively. Throughout this section, we will assume that the time series within the donor pool are independent. This is needed for exact variance expressions. However, the theory developed later allows for dependence within the donor pool \red{be specific of when independence is required and when it is not}. Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below:

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since MacBook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of MacBooks account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. after the release of the latest MacBook on November, 10th, 2020. Our donor pool suggests that it takes two days for the shock effect to take hold. Therefore, we are interested in the stock price of Apple Inc. on the day after the release date, i.e., on November 11th, 2020. Our data is collected using the \texttt{quantmod} package \citep{ryan2017quantmod} in R. The detailed considerations of our analysis are outlined as below:

\begin{enumerate}[label = (\arabic*)]
  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc. All the estimates will be adjusted for inflation.  We consider $D_{i, t} = I(t = T_i^*+2)$. By observing  the data, we found a large shock effect on October 10th, 2020, two days before the release of iPhone 12, iPhone 12 Pro, MagSafe accessories, and HomePod mini. Denote this date by $T_{1,\#}$, and the shock effect by $\beta$. We account for this shock effect that is not of our interest in the model by setting 
  \begin{align*}
    y_{1,t} &= \eta_i + \alpha_1 D_{1,t} +\phi_1y_{1, t-1}+\theta_1'\mathbf{x}_{1,t} + \beta I(t = T_{1,\#}) + \varepsilon_{i,t}.
  \end{align*}
  The model for the shock effect is
  \begin{align*}
    \alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{i,T_i^*+2}  + \tilde{\varepsilon}_{i,t}.
  \end{align*}
  Then, the weighting schemes introduced in Section \ref{constructionofestimators} will use  $\{\mathbf{x}_{i,T_i^*+2} \colon i = 1, \ldots, n+1\}$ for computing $\mathbf{W}^*$, where $\mathbf{x}_{1, T_1^*+2}$ will require prediction as detailed in (2) Selection of covariates. We used mean squared error for the response in the training data to select an appropriate time length out of 20, 25, 30, and 50 trading days. As a result, we consider 25 trading days data for the time series of interest and time series in the donor pool. 
  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates. We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. We then predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date in the middle of 25 trading days for 2017, 2018, and 2019.  The specific shock-effect dates are June 6th, 2017, October 30th, 2018, and June 3rd, 2019, respectively. We only include the last three MacBook releases in our donor pool. This is because these releases are similar to the current release, Apple inc. has only updated the hardware of the computer without much redesign of the MacBook \citep{apple2017, apple2018, apple2019}. The same is the case with the lastest MacBook release \citep{apple2020}.  %The new MacBook series is built with M1 chip invented by Apple inc. instead of chips by Intel inc. that were used in past years, and their CPU speed improves significantly \citep{apple2020}. 
\end{enumerate}

@@

Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its second moments exist. The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.  Additionally, $\alpha_i$ can be heteroskedastic; i.e.,  they can have different variances. In this scenario, all the theoretical properties still hold though variance expressions in Section \ref{conditions} may not apply. We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts. An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis. Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.

@@

We can extend the proposed methodology to forecast the response $m\geq 2$ time points ahead. %We present one possible generalization under the specification that $m = 2$. 
In this setting, there are two cases. In the first case, we suppose that there is no additional shock after $T_1^*+1$. Then, the forecast boils down to standard $m$-ahead forecast in time series. In the second case, we assume that the time series under study will experience an additional additive shock at $T_1^* + m$, say $\alpha_1^{(m)}$. Users now construct the donor pool to consist of time series that experience shocks similar to  $\alpha_1^{(m)}$. Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(m)}$.  The adjusted forecast at $t = T_1^* + m$ is
$
  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}.
$

@@

Construction of the donor pool is a critical step that directly matters in prediction. In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for  varying variances and  varying means that are linear functions of common covariates. Remark \ref{remark1} shows that common covariates are not restrictive with structural zero in coefficients. However, it is difficult to verify such assumption or structure in practice. In principle, one should select individuals that come from a common population, the same populationas the individual under study, to form the donor pool. This selection criterion is often adopted in the literature of comparative case studies. For example, \citet{card1990impact} used a set of cities in southern U.S. to estimate the effect of 1980 Mariel Boatlift on the Miami labor market. \citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country. To estimate the effect of Proposition 99, a large tobacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period. Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.

@@

@@

\noindent \textbf{Case II: under $\mc{M}_{21}$ and $\mc{M}_{22}$:} Since $\E{\tilde{\varepsilon}_{i, T_i}}=0$, $\E{\hat{\tilde{\alpha}}_{i}}=\E{\tilde{\alpha}_{i}}=\E{\alpha_{i}}$, it follows that
  \begin{align*}
   \E{\hat{\alpha}_{\rm wadj}}
   &= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}\\
   &= \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right)\\
   &= \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}\right]\bigg\}\\
   &=\mu_{\alpha}+ \mu_{\delta}' \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}\tag{$\mbf{W}\in \mc{W}$}
   \\
   &=\mu_{\alpha}+  \mu_{\delta}'\mbf{x}_{1, T_1^*+1}. \tag{from (\ref{SCM})}
   \end{align*}
Similarly,
  \begin{align*}
   \E{\hat{\alpha}_{\rm adj}}
   &=\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \mu_{\delta}'  \mbf{x}_{i, T_i^*+1}.
   \end{align*}

@@

Notice that under the setting of OLS, the design matrix for $\mc{M}_2$ is the same as the one for $\mc{M}_1$. Therefore, it follows that
  \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \E{\var{\hat{\alpha}_{\rm wadj}|\Theta}} + \var{\E{\hat{\alpha}_{\rm wadj}|\Theta}} \\
  &=\mrm{E} \left\{\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\} +\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
\end{align*}
Under $\mc{M}_{21}$ where $\delta_i=\delta$ are fixed unknown parameters,  we will have
  \begin{align}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma_i^2(\mbf{M}'_i\mbf{M}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
\end{align}
Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \varepsilon_{i,t}$, we have
 \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
 & \quad  + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
\end{align*}
For the adjustment estimator, we simply replace $\mbf{W}^*$ with $1/n\mbf{1}_n$. Thus, under $\mc{M}_{21}$ we have 
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{1}{n^2}\sum_{i=2}^{n+1} \sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
\end{align*}
Under $\mc{M}_{22}$, we shall have
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}\\
  & \quad  +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
Notice that $\mc{M}_{1}$ differs from $\mc{M}_{21}$ only by its mean parameterization of $\alpha$ (see Section \ref{modelsetup}). In other words, the variances of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ under $\mc{M}_1$ are the same for those under $\mc{M}_{21}$.

@@

\subsection{Tables for Section \ref{simulation}}
\label{tablesappendix}
\newpage

>>>>

\red{Check out this paragraph.} In our methodological framework, the researcher first creates a donor pool of time series which have undergone similar structural shocks in the past. Similarity in this context refers to the shock effects as arising from a common distribution with existing second moments. The unobserved shock effect in the time series of interest is assumed to arise from the same distribution. Construction of the donor pool and the desired aims of the donor pool has precedent in synthetic control methodology (SCM) \citep{abadie2010synthetic}. As in SCM, care is needed when forming the donor pool of time series. However, there are several key differences between our framework and SCM. Unlike in SCM, we are not trying to estimate the causal effect of an intervention. Also, we assume that the time series forming the donor pool are independent from the time series under study before the timing of the shock. This rules out panel data applications where the time series of interest and those forming the donor pool evolve in tandem. When there are large time differences between the time series under study and those forming the donor pool, then the dependence will be negligible in practice. This is the case in the Conoco Phillips and Apple stock forecasting examples.

We then estimate the shock effects that are present in the time series forming the donor pool for which the post-shock responses are observed. These estimated shock effects are then aggregated. Finally, this aggregated estimator is added to the forecast for the yet to be realized post-shock response of the time series of interest. Our adjustment is similar to various adjustment methodologies suggested by \cite{clements1996intercept} that use the residual at end of observed time horizon for $h$-ahead forecasts. However, the approach of \cite{clements1996intercept} is not robust to unprecedented and unobserved shock since the shock signal is not embedded in the data. Under a similar setting that studies equilibrium shifts, \cite{castle2015robust} propose robust general approaches for forecasting in vector equilibrium-correction models. However, their forecasting methodology requires conditioning on the past data that contain shock signals. This approach is therefore not applicable in the post-shock setting. The shock effects in our post-shock forecasting framework are similar to ``expectation shocks,'' studied in \cite{clements2019measuring}. \cite{clements2019measuring} allows for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach, as in \cite{croushore2006data}. In our context, the yet to be observed shock effect of interest arises as a random effect whose assumed generative distribution can only be partially estimated. This partial estimation only uses shock effect estimates from the time series forming the donor pool.

In this article, we will assume a simple autoregressive data generating process  with a general random-effect structure. These specifications are similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical}. In our model, the donor pool can consist of dependent time series, but the time series forming the donor pool are required to be independent from the time series of interest. However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method. We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in SCM \citep{abadie2010synthetic}. The considered adjustment strategies all target the mean of the shock effect distribution. Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop. We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design.  We demonstrate the utility of our methodology with two real data analyses. The first of these focuses on forecasting the stock price of Conoco Phillips after March 9th, 2020, in the midst of the COVID-19 pandemic and an oil supply war. The second of these focuses on forecasting the stock price of Apple Inc. after the company releases their latest installment of the MacBook on November 10th, 2020. We will show that our proposed adjustment estimators yield much better results than no adjustment in these examples. The Conoco Phillips example provides an empirical application of our methods when the shock is unprecedented in nature, arising from a global pandemic and an oil supply shock. The Apple example provides a case for post-shock prediction when the shock has precedent, Apple just released the latest version of their MacBook product. We now elaborate our framework for post-shock prediction.

@@

Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple conditions for risk-reduction to hold, and more importantly motivates a bootstrap estimation procedure for evaluation of these conditions, discussed in Section \ref{conditions} and \ref{varbootstrap} respectively. Throughout this section, we have specified that the time series within the donor pool are independent. This is needed for exact variance expressions. However, the theory developed later allows for dependence within the donor pool. Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below:

@@

Apple Inc. is an American technology company that develops a range of electronics and software with typical products such as, iPhone, iPad, Mac, and Apple Watch. Every year, Apple Inc. releases a new series of MacBook computers to the public. Typically, after the release, the stock price of Apple Inc. is expected to experience a shock since MacBook sales is one of the most profitable line of Apple Inc.'s business and investors are likely to adjust their investment decisions based on the new features introduced. For example, the sales of MacBooks account for 9.8\% of its revenue \citep{applemac}. In this example, we are interested in forecasting the stock price of Apple Inc. after the release of the latest MacBook on November, 10th, 2020. Our donor pool suggests that it takes two days for the shock effect to take hold. Therefore, we are interested in the stock price of Apple Inc. on the day after the release date, November 11th, 2020. Our data is collected using the \texttt{quantmod} package \citep{ryan2017quantmod} in R. The detailed considerations of our analysis are outlined as below:

\begin{enumerate}[label = (\arabic*)]
  \item \textbf{Selection of model.}  We use an AR(1) model to forecast the stock price of Apple Inc. All the estimates will be adjusted for inflation.  We consider $D_{i, t} = I(t = T_i^*+2)$. By observing  the data, we found a large shock effect on October 10th, 2020, two days before the release of iPhone 12, iPhone 12 Pro, MagSafe accessories, and HomePod mini. Denote this date by $T_{1,\#}$, and the shock effect by $\beta$. We account for this shock effect that is not of our interest in the model by setting 
  \begin{align*}
    y_{1,t} &= \eta_i + \alpha_1 D_{1,t} +\phi_1y_{1, t-1}+\theta_1'\mathbf{x}_{1,t} + \beta I(t = T_{1,\#}) + \varepsilon_{i,t}.
  \end{align*}
  The model for the shock effect is
  \begin{align*}
    \alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{i,T_i^*+2}  + \tilde{\varepsilon}_{i,t}.
  \end{align*}
  Then, the weighting schemes introduced in Section \ref{constructionofestimators} will use  $\{\mathbf{x}_{i,T_i^*+2} \colon i = 1, \ldots, n+1\}$ for computing $\mathbf{W}^*$, where $\mathbf{x}_{1, T_1^*+2}$ will require prediction as detailed in (2) Selection of covariates. We used mean squared error for the response in the training data to select an appropriate time length out of 20, 25, 30, and 50 trading days. As a result, we consider 25 trading days data for the time series of interest and time series in the donor pool. 
  \item \textbf{Selection of covariates.} We consider lagged  S\&P 500 index prices and 13 Week treasury bill rates as covariates. In this example, the weighting method will require future covariates in computation. As a result, forecasting of future covariates is needed. We used AIC to select an AR(3) model for forecasting the S\&P 500 index prices and an AR(1)   model for forecasting the 13 Week treasury bill rates. We used Ljung-Box test to test  model adequacy for 10 lags and failed to reject the null hypothesis that autocorrelation does not exist in the residuals series of the corresponding models. We then predict the future covariates.
  \item \textbf{Construction of donor pool.} Our donor pool consists of the time series data of Apple Inc. with shock-effect date in the middle of 25 trading days for 2017, 2018, and 2019.  The specific shock-effect dates are June 7th, 2017, October 31st, 2018, and June 4th, 2019, respectively. We only include the last three MacBook releases in our donor pool. This is because these releases are similar to the current release, Apple inc. has only updated the hardware of the computer without much redesign of the MacBook \citep{apple2017, apple2018, apple2019}. The same is the case with the latest MacBook release \citep{apple2020}.  %The new MacBook series is built with M1 chip invented by Apple inc. instead of chips by Intel inc. that were used in past years, and their CPU speed improves significantly \citep{apple2020}. 
\end{enumerate}

@@

Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its second moments exist. The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.  Additionally, $\alpha_i$ can be heteroskedastic. In this scenario, all the theoretical properties still hold though variance expressions in Section \ref{conditions} may not apply. We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts. An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis. Our methodology is developed for autoregressive models, but it can be generalized to any setting  where model parameters can be estimated unbiasedly, there is an additive shock-effect structure, and the time series in the donor pool are independent from the one of interest.

@@

We can extend the proposed methodology to forecast the response $m\geq 2$ time points ahead. In this setting, there are two cases. In the first case, we suppose that there is no additional shock after $T_1^*+1$. Then, the forecast boils down to standard $m$-ahead forecast in time series. In the second case, we assume that the time series under study will experience an additional additive shock at $T_1^* + m$, say $\alpha_1^{(m)}$. Users now construct the donor pool to consist of time series that experience shocks similar to  $\alpha_1^{(m)}$. Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(m)}$.  The adjusted forecast at $t = T_1^* + m$ is
$
  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}
$
where the future covariates are themselves forecasted. The additional forecasting variability may  render such an adjustment approach useless.

In our framework we have assumed the covariates to be known. However, it may be the case that the shock effects the covariates as well as the response. If so, one may be able to consider forecast scenarios (or conditional forecasts) \citep{baumeister2014real} to make post-shock predictions. In this setting, one would need to produce a grid of likely $\mathbf{x}_{1, T_1^* + 1}$ values to proceed. A post-shock prediction can be made for every hypothetical $\mathbf{x}_{1, T_1^* + 1}$ value forming the previously mentioned grid. This yields a range of post-shock predictions whose validity is subject to the accuracy of the $\mathbf{x}_{1, T_1^* + 1}$ values forming the grid. This may gives users a sense of the variability of post-shock predictions due to forecast error from covariates that are also affected from the shock.

@@

Construction of the donor pool is a critical step in our post-shock prediction framework. In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for varying variances and  varying means that are linear functions of common covariates. However, it may be difficult to confirm such an assumption or modeling structure in practice. Also note that we assume that the time series under study is independent of those forming the donor pool, independence being practically satisfied when the time series of interest is separated from the donor pool in time. In principle, one should select time series that come from a common population, the same population as the individual under study, to form the donor pool. This selection criterion is often adopted in the literature of comparative case studies. For example, \citet{card1990impact} used a set of cities in southern U.S. to estimate the effect of 1980 Mariel Boatlift on the Miami labor market. \citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country. To estimate the effect of Proposition 99, a large tobacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period. Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.

@@

%\section{Acknowledgements}

@@

\noindent \textbf{Case II: under $\mc{M}_{21}$ and $\mc{M}_{22}$:} Since $\E{\tilde{\varepsilon}_{i, T_i}}=0$, $\E{\hat{\tilde{\alpha}}_{i}}=\E{\tilde{\alpha}_{i}}=\E{\alpha_{i}}$, it follows that
  \begin{align*}
   \E{\hat{\alpha}_{\rm wadj}}
   &= \mrm{E}\left\{\mrm{E}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\}
   = \mrm{E}\left( \sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
   = \mrm{E}\bigg\{ \sum_{i=2}^{n+1} w_i^*\left[\mu_{\alpha}+\delta_{i}'\mbf{x}_{i, T_i^*+1}\right]\bigg\} \\
   &=\mu_{\alpha}+ \mu_{\delta}' \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}\tag{$\mbf{W}\in \mc{W}$}
   \\
   &=\mu_{\alpha}+  \mu_{\delta}'\mbf{x}_{1, T_1^*+1}. \tag{from (\ref{SCM})}
   \end{align*}
Similarly,
$
   \E{\hat{\alpha}_{\rm adj}}
   =\mu_{\alpha}+\frac{1}{n}\sum_{i=2}^{n+1} \mu_{\delta}'  \mbf{x}_{i, T_i^*+1}.
$

@@

Notice that under the setting of OLS, the design matrix for $\mc{M}_2$ is the same as the one for $\mc{M}_1$. Therefore, it follows that
  \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \E{\var{\hat{\alpha}_{\rm wadj}|\Theta}} + \var{\E{\hat{\alpha}_{\rm wadj}|\Theta}} \\
  &=\mrm{E} \left\{\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i|\Theta\right)\right\} +\mrm{Var}\left(\sum_{i=2}^{n+1} w_i^*\alpha_i\right) 
\end{align*}
Under $\mc{M}_{21}$ where $\delta_i=\delta$ are fixed unknown parameters,  we will have
  \begin{align}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \mrm{E} \left\{\sum_{i=2}^{n+1}(w_i^*)^2(\sigma_i^2(\mbf{M}'_i\mbf{M}_i)^{-1}_{22})\right\} +\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2  \nonumber\\
  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2.\label{equation6}
\end{align}
Similarly, under $\mc{M}_{22}$ where we assume $\delta_i \indep \varepsilon_{i,t}$, we have
 \begin{align*}
  \var{\hat{\alpha}_{\rm wadj}} 
  &= \sum_{i=2}^{n+1}(\sigma_i w_i^*)^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\} + \sum_{i=2}^{n+1} (w_i^*)^2 (\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha})
\end{align*}
For the adjustment estimator, we simply replace $\mbf{W}^*$ with $1/n\mbf{1}_n$. Thus, under $\mc{M}_{21}$ we have 
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{1}{n^2}\sum_{i=2}^{n+1} \sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2}
\end{align*}
Under $\mc{M}_{22}$, we shall have
 \begin{align*}
  \var{\hat{\alpha}_{\rm adj}} 
  =\frac{1}{n^2}\sum_{i=2}^{n+1}\sigma_i^2\mrm{E}\big\{(\mbf{M}'_i\mbf{M}_i)^{-1}_{22}\big\}
   +\frac{1}{n^2}(\mbf{x}_{i, T_i^*+1}'\Sigma_{\delta}\mbf{x}_{i, T_i^*+1} + \sigma^2_{\alpha}).
\end{align*}
Notice that $\mc{M}_{1}$ differs from $\mc{M}_{21}$ only by its mean parameterization of $\alpha$ (see Section \ref{modelsetup}). In other words, the variances of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ under $\mc{M}_1$ are the same for those under $\mc{M}_{21}$.

@@

\subsection{Tables for Section \ref{simulation}}
\label{tablesappendix}
